---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {rjts}

<!-- badges: start -->
[![R-CMD-check Build
Status](https://github.com/brownag/rjts/workflows/R-CMD-check/badge.svg)](https://github.com/brownag/rjts/actions)
[![rjts
Manual](https://img.shields.io/badge/docs-HTML-informational)](https://humus.rocks/rjts/)
<!-- badges: end -->

The goal of {rjts} is to provide a basic {rJava} wrapper for the JTS Topology Suite <<https://www.osgeo.org/projects/jts/>>.

Check out the Javadoc <<https://locationtech.github.io/jts/javadoc/>> to see the tools that are provided via JTS.

## Installation

You can install the development version of {rjts} with {remotes}

``` r
if (!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("brownag/rjts")
```

Once the package is installed, you will need to install the required JAR files.

```r
library(rjts)
#> rjts (#.#.#) -- R interface to the JTS Topology Suite
#> 
#>   Unable to load JTS JAR files! Perhaps the package was installed with an empty 'inst/java' directory?
#>                    
#>    - Run `install_jts()` to download libraries from GitHub <https://github.com/locationtech/jts/releases>
#>                    
#>    - Then, re-install the package. It may be convenient to use a local instance of the GitHub repository to install from.
```

You can download and install JAR libraries from GitHub <<https://github.com/locationtech/jts/releases>> with `install_jts()`. You will need to run this installation command in a _local_ instance of the package repository that you can then install the package from (again). 

For instance, you can do:

```sh
git clone http://github.com/brownag/rjts.git
Rscript -e "rjts::install_jts('rjts')"
Rscript -e "remotes::install_local('rjts', force = TRUE)"
```

This clones the Git repository and enters it, runs `install_jts()` (requires {rjts} be installed from GitHub as above), then runs `remotes::install_local()` to _re-install_ from the local instance of the package (where `"inst/java"` has been populated with relevant JAR files).

```r
library(rjts)

#> rjts (#.#.#) -- R interface to the JTS Topology Suite
#> Added JTS version #.#.# to Java classpath
#>   JAR files:
#>      jts-core-#.#.#.jar
#>      JTSTestBuilder.jar
```

## Example

This is an example showing how to read and write Well-Known Text (WKT) and Well-Known Binary. You can perform various basic geometric operations by accessing [`Geometry`](https://locationtech.github.io/jts/javadoc/org/locationtech/jts/geom/Geometry.html) class methods exposed in the `read()` result object. Use `$` to access methods.

```{r example}
library(rjts)

wr <- WKTReader()

# read a MULTIPOLYGON from character vector
x <- wr$read("MULTIPOLYGON (((40 40, 20 45, 45 30, 40 40)),
                           ((20 35, 10 30, 10 10, 30 5, 45 20, 20 35),
                           (30 20, 20 15, 20 25, 30 20)))")
x$getGeometryType()

# use the WKTWriter to return Well-known text
ww <- WKTWriter()
ww$writeFormatted(x$convexHull())

wb <- WKBWriter()
y <- wb$write(x$convexHull())

class(y)
y

wbr <- WKBReader()
wbr$read(y)

# Geometry objects/results also have a toString() method that returns WKT
x$getBoundary()$toString()
x$convexHull()$toString()
```
